---
title: "Lecture 11-12 - R markdown"
author: "Tamas Nagy"
date: "December 7, 2017"
output: html_document
---
# How to write an R markdown document

In an R markdown document, you can have a normal text (written using markdown), code blocks, output blocks, embedded pictures (even animgifs ;). 

Use standard r markdown notation:

# Heading 1
## Heading 2
### Heading 3
#### Heading 4
##### Heading 5


You can draw a horizontal separator like this:

-------------------

When you want to put things in separate lines, use double enter (one empty line) between items

Bold: *italic*

Italic: **bold**

Strike-through: ~~strike-through~~ 

Use bullet points:

* like this
* or this
* or his
- or this (* and - are interchangeable as bullet points)

Or numbering:

1. First
2. Second
3. Third
    a. can
    b. have
    c. hierarchies
    

-------------------------------
There are some useful keyboard shortcuts:

* Ctrl/Cmd + Shift + K Saves your document and compiles it to html (or pdf or docx, depending on your setting)
* F7 performs a spell check on the text (not the code)
* If you just want to run a code chunk, use Ctrl/Cmd + Enter

```{r setup, include=FALSE}
library(tidyverse)
if (!require(babynames)) install.packages("babynames")
library(babynames)
```

```{r}
babynames
```

